# Package

```{r}
packages <- c(
  "ggplot2", "dplyr", "tidyverse", "readr", "car",
  "janitor", "skimr", "lme4", "lmerTest", "emmeans",
  "multcomp", "multcompView", "ggResidpanel"
)

# Install only the ones not already installed
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages)

# Then load them all
lapply(packages, library, character.only = TRUE)

install.packages("remotes")
remotes::install_github("goodekat/ggResidpanel")
```

# count sample size per treatment combination
```{r}
raw_data <-read.csv("raw_data.csv")

raw_data %>%
  group_by(Mum_temp, Dad_temp,Sex, OS_temp,OS_age)  %>%
  summarise(total_n = n(),
            .groups = "drop") 
```

# PO activity
```{r}
## Read file
po <- read.csv("raw_data.csv") %>%
  clean_names() %>%     # change the variable names: convert to lowercase with underscores
  mutate(os_temp = factor(os_temp, levels = c("C", "H"), 
                          labels = c("ancestral", "high")),
         mum_temp = factor(mum_temp, levels = c("C", "H"),
                           labels = c("ancestral", "high")),
         dad_temp = factor(dad_temp, levels = c("C", "H"),
                           labels = c("ancestral", "high")),
         sex = factor(sex, levels = c("F", "M"),
                      labels = c("female", "male")),
         os_age = factor(os_age, levels = c("1", "3", "5", "7"), 
                         ordered = TRUE))   # modify offspring age as an ordered factor

## Tidy data
po_clean <- po %>%
  filter(!is.na(po_activity)) # remove rows where PO activity is not available


## Standardize PO activity

# To standardize the PO activity across the plates, PO activity was divided by the inter-plate control and followed by a log-transformation. The standardized immune response was stored as log_po_corrected

po_corrected <- po_clean %>%
  group_by(po_plate_id) %>%
  mutate(
    log_po_corrected = log(po_activity / po_interplate) # Compute standardized PO activity
    ) %>% 
  group_by(.groups = "drop") 

# Use Q-Q plot to check the normality of standardized PO activity.
library(ggplot2)
ggplot(po_corrected, aes(sample = log_po_corrected)) +
  stat_qq() +
  stat_qq_line(col = "red") +
  theme_classic()

## Separate dataset by sex (PO activity)

# female data
female_po <- po_corrected [po_corrected$sex == "female", ]

# male data
male_po <- po_corrected [po_corrected$sex == "male", ]

```

## Female analysis (PO activity)
```{r}
# Full model: with all possible interactions

F_model_po_full <- lmer(log_po_corrected ~ mum_temp * dad_temp * os_temp + os_age + weight + (1 | mother),
  data = female_po) # response variable is log(po activity) after standardize. random variable is mother (means family id)

summary (F_model_po_full)
Anova(F_model_po_full, type = 3)
resid_panel(F_model_po_full)

# Reduced model: excluding the non-significant three-way interaction

F_model_po_2 <- lmer(log_po_corrected ~ mum_temp * dad_temp + mum_temp * os_temp + dad_temp * os_temp + os_age + weight + (1 | mother),
  data = female_po) # response variable is log(po activity) after standardize. random variable is mother (means family id)

summary (F_model_po_2)
Anova(F_model_po_2, type = 3)

# Final model: excluding the non-significant two-way interactions

F_model_po_3 <- lmer(log_po_corrected ~ mum_temp + dad_temp + os_temp + os_age + weight + (1 | mother),
  data = female_po) # response variable is log(po activity) after standardize. random variable is mother (means family id)

summary (F_model_po_3)
Anova(F_model_po_3, type = 3)

# model comparison
anova (F_model_po_full, F_model_po_3, REML = FALSE)

```
## Figure - Female PO activity 
```{r}
######################
### offspring temp ### (Figure 2A)
######################

F1 <- ggplot(female_po, aes(x = os_temp, y = log_po_corrected)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(aes(colour = os_temp),
              width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("ancestral" = "blue",
                                 "high" = "red")) +
  scale_x_discrete(labels = c("ancestral" = "control",
                              "high" = "high")) +
  labs(x = "offspring temp",
       y = "PO_corrected") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )

F1 + scale_y_continuous(limits = c(-4.2, 4),
                   breaks = seq(-4, 4, 2))

# count sample size                   
female_po%>%
  group_by(os_temp)  %>%
  summarise(total_n = n(),
            .groups = "drop") 

#######################
### mum-by-dad temp ### (Figure 3A)
#######################
F1.1 <- ggplot(female_po, aes(x = interaction (dad_temp, mum_temp), y = log_po_corrected)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(aes(colour = dad_temp),
              width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("ancestral" = "blue",
                                 "high" = "red")) +
                                 scale_x_discrete(labels = c("ancestral.ancestral" = "control",
                            "ancestral.high" = "control",
                            "high.ancestral" = "high",
                            "high.high" = "high")) + labs(x = "dad-mum_temp",
       y = "PO_corrected") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )

F1.1

# count sample size                    
female_po%>%
  group_by(mum_temp, dad_temp)  %>%
  summarise(total_n = n(),
            .groups = "drop") 

```            

## Male analysis (PO activity)
```{r}
# Full model: with all possible interactions

M_model_po_full <- lmer(log_po_corrected ~ mum_temp * dad_temp * os_temp + os_age + weight + (1 | mother),
  data = male_po) # response variable is log(po activity) after standardize. random variable is mother (means family id)

summary (M_model_po_full)
Anova(M_model_po_full, type = 3)
resid_panel(M_model_po_full)

# Reduced model: excluding the non-significant three-way interaction

M_model_po_2 <- lmer(log_po_corrected ~ mum_temp * dad_temp + mum_temp * os_temp + dad_temp * os_temp + os_age + weight + (1 | mother), data = male_po) # response variable is log(po activity) after standardize. random variable is mother (means family id)

summary (M_model_po_2)
Anova(M_model_po_2, type = 3)
resid_panel(M_model_po_2)

# Final model: excluding the non-significant two-way interactions

M_model_po_3 <- lmer(log_po_corrected ~ mum_temp * dad_temp + os_temp + os_age + weight + (1 | mother), data = male_po) # response variable is log(po activity) after standardize. random variable is mother (means family id)

summary (M_model_po_3)
Anova(M_model_po_3, type = 3)
resid_panel(M_model_po_3)

# model comparison
anova (M_model_po_full, M_model_po_3, REML = FALSE)

# pairwise analysis, given an interaction between mom * dad temperature
em1 <- emmeans(M_model_po_3, ~ mum_temp * dad_temp)

pairs(em1, adjust = "tukey")
summary(em1)
```

## Figure - Male PO activity 
```{r}
####################
## Offspring temp ## (Figure 2A)
####################

M1 <- ggplot(male_po, aes(x = os_temp, y = log_po_corrected)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(aes(colour = os_temp),
              width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("ancestral" = "blue",
                                 "high" = "red")) +
  scale_x_discrete(labels = c("ancestral" = "control",
                              "high" = "high")) +
  labs(x = "offspring temp",
       y = "PO_corrected") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )

M1 + scale_y_continuous(limits = c(-4.2, 4),
                   breaks = seq(-4, 4, 2))

# count sample size 
male_po%>%
  group_by(os_temp)  %>%
  summarise(total_n = n(),
            .groups = "drop")

#######################
### mum-by-dad temp ### Figure 3B
#######################
M1.1 <- ggplot(male_po, aes(x = interaction (dad_temp, mum_temp), y = log_po_corrected)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(aes(colour = dad_temp),
              width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("ancestral" = "blue",
                                 "high" = "red")) +
                                 scale_x_discrete(labels = c("ancestral.ancestral" = "control",
                            "ancestral.high" = "control",
                            "high.ancestral" = "high",
                            "high.high" = "high")) + labs(x = "dad-mum_temp",
       y = "PO_corrected") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )

M1.1

# count sample size 
male_po%>%
  group_by(mum_temp, dad_temp)  %>%
  summarise(total_n = n(),
            .groups = "drop") 
```

## Additional analysis by replacing 'maternal-by-paternal temperature combinations' with the matching between maternal and paternal temperatures
```{r}
## Create a new column depending on temperature matching between maternal and paternal temperatures
library(dplyr)

male_po <- male_po %>%
  mutate(matchiness = case_when(
    mum_temp == dad_temp ~ "matched",
    mum_temp != dad_temp ~ "mismatched"
  ))

## Additional model (Replacing "mum_temp" and "dad_temp" with "matchiness" in the final male model)
M_model_po_4 <- lmer(log_po_corrected ~ matchiness + os_temp + os_age + weight + (1 | mother), data = male_po) 
summary (M_model_po_4)
Anova(M_model_po_4, type = 3)
resid_panel(M_model_po_4)

emmeans(M_model_po_4, ~ matchiness) %>%
  pairs(adjust = "tukey")

## Figure (Figure S2)
M2 <- ggplot(male_po, aes(x = matchiness, y = log_po_corrected, color = matchiness)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("matched" = "orange",
                                 "mismatched" = "purple")) +
  labs(x = "The consistency of parental temperature",
       y = "Male PO activity \n(log-transformed)") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )+ 
  scale_y_continuous(limits = c(-4.2, 4),
                   breaks = seq(-4, 4, 2)) +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )

# count sample size 
male_po%>%
  group_by(matchiness)  %>%
  summarise(total_n = n(),
            .groups = "drop")
```

## Lytic activity
```{r}
## Read file
lytic <- read.csv("raw_data.csv") %>%
  clean_names() %>%
  mutate(os_temp = factor(os_temp, levels = c("C", "H"), 
                          labels = c("ancestral", "high")),
         mum_temp = factor(mum_temp, levels = c("C", "H"),
                           labels = c("ancestral", "high")),
         dad_temp = factor(dad_temp, levels = c("C", "H"),
                           labels = c("ancestral", "high")),
         sex = factor(sex, levels = c("F", "M"),
                      labels = c("female", "male")),
         os_age = factor(os_age, levels = c("1", "3", "5", "7"), 
                         ordered = TRUE)
         ) %>% mutate(zone_area_2 = as.numeric(zone_area_2))

## Tidy data (lytic)
# step 1
lytic_clean <- lytic %>%
  filter(!is.na(zone_area_1))

summary(lytic_clean)

# step 2: calculate the mean zone area
lytic_clean <- lytic_clean %>%
  mutate(zone_area = (zone_area_1 + zone_area_2 + zone_area_3)/3)

## Standardise data (lytic)
lytic_corrected <- lytic_clean %>%
  group_by(lytic_plate_id) %>%
  mutate(lytic_corrected = zone_area / lytic_interplate) %>%  # Compute standardized lytic activity

  group_by(.groups = "drop") 

## Separate dataset by sex (lytic)

# female data
female_ly <- lytic_corrected [lytic_corrected$sex == "female", ]

# male data
male_ly <- lytic_corrected [lytic_corrected$sex == "male", ]

```

## Female analysis (lytic)
```{r}
# change the order to present zone clearity result:
female_ly$zone_clarity <- relevel(factor(female_ly$zone_clarity), ref = "super_clear")

# Full model: with all possible interactions

F_model_ly_full <- lmer(lytic_corrected ~ mum_temp * dad_temp * os_temp + os_age + weight + zone_clarity + (1 | mother),
  data = female_ly)

summary (F_model_ly_full)
Anova(F_model_ly_full, type = 3)
resid_panel(F_model_ly_full)

# Reduced model: excluding the non-significant three-way interaction

F_model_ly_2 <- lmer(lytic_corrected ~ mum_temp * dad_temp +  mum_temp * os_temp + dad_temp * os_temp + os_age + weight + zone_clarity + (1 | mother),
  data = female_ly)

summary (F_model_ly_2)
Anova(F_model_ly_2, type = 3)
resid_panel(F_model_ly_2)

# Final model: excluding the non-significant two-way interactions

F_model_ly_3 <- lmer(lytic_corrected ~ mum_temp + dad_temp + os_temp + os_age + weight + zone_clarity + (1 | mother),
  data = female_ly)

summary (F_model_ly_3)
Anova(F_model_ly_3, type = 3)
resid_panel(F_model_ly_3)

# model comparison
anova (F_model_ly_full, F_model_ly_3, REML = FALSE)
```
## Figure - femaly lytic
```{r}
####################
## offspring temp ## (Figure 2B)
####################
library(ggplot2)
F2 <- ggplot(female_ly, aes(x = os_temp, y = lytic_corrected)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(aes(colour = os_temp),
              width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("ancestral" = "blue",
                                 "high" = "red")) +
  scale_x_discrete(labels = c("ancestral" = "control",
                              "high" = "high")) +
  labs(x = "offspring temp",
       y = "lytic_corrected") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )

F2 + scale_y_continuous(limits = c(0.5, 1.5),
                   breaks = seq(0.5, 1.5, 0.25))

# count sample size
female_ly%>%
  group_by(os_temp)  %>%
  summarise(total_n = n(),
            .groups = "drop")     

```

## Male analysis (lytic)
```{r}

# change the order to present zone clearity result:
male_ly$zone_clarity <- relevel(factor(male_ly$zone_clarity), ref = "super_clear")


# Full model: with all possible interactions

M_model_ly_full <- lmer(lytic_corrected ~ mum_temp * dad_temp * os_temp + os_age + weight + zone_clarity + (1 | mother),
  data = male_ly)

summary (M_model_ly_full)
Anova(M_model_ly_full, type = 3)
resid_panel(M_model_ly_full)

# Reduced model: excluding the non-significant three-way interaction

M_model_ly_2 <- lmer(lytic_corrected ~ mum_temp * dad_temp +  mum_temp * os_temp + dad_temp * os_temp + os_age + weight + zone_clarity + (1 | mother),
  data = male_ly)

summary (M_model_ly_2)
Anova(M_model_ly_2, type = 3)
resid_panel(M_model_ly_2)

# Final model: excluding the non-significant two-way interactions

M_model_ly_3 <- lmer(lytic_corrected ~ mum_temp + dad_temp + os_temp + os_age + weight + zone_clarity + (1 | mother),
  data = male_ly)

summary (M_model_ly_3)
Anova(M_model_ly_3, type = 3)
resid_panel(M_model_ly_3)

# model comparison
anova (M_model_ly_full, M_model_ly_3, REML = FALSE)
```

## Figure - male lytic
```{r}
###########################
## offspring temperature ## Figure 2B
###########################

library(ggplot2)
M2 <- ggplot(male_ly, aes(x = os_temp, y = lytic_corrected)) +
  geom_violin(colour = "black",
              alpha = 0.6,
              width = 0.5) +
  geom_jitter(aes(colour = os_temp),
              width = 0.1,
              alpha = 0.05,
              size = 1.5) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = 0.15,
               colour = "black",
               linewidth = 1) +
  scale_colour_manual(values = c("ancestral" = "blue",
                                 "high" = "red")) +
  scale_x_discrete(labels = c("ancestral" = "control",
                              "high" = "high")) +
  labs(x = "offspring temp",
       y = "lytic_corrected") +
  theme_classic() +
  theme(
    axis.line = element_blank(),
    panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1),
    legend.position = "none"
  )
M2 + scale_y_continuous(limits = c(0.5, 1.5),
                   breaks = seq(0.5, 1.5, 0.25))

# count sample size 
male_ly%>%
  group_by(os_temp)  %>%
  summarise(total_n = n(),
            .groups = "drop")      

```

# effect size (cohens'd)
```{r}
library(dplyr)
library(effectsize)

####################################
### offspring temp _ PO activity ###
####################################

# Cohen's d
f_eff_po <- cohens_d(log_po_corrected ~ os_temp, data = female_po)
m_eff_po <- cohens_d(log_po_corrected ~ os_temp, data = male_po)

f_eff_po
m_eff_po

# Extract d values
d_f_po <- f_eff_po$Cohens_d[1]
d_m_po <- m_eff_po$Cohens_d[1]

# Sample sizes per os_temp group
f_n_po <- female_po %>%
  group_by(os_temp) %>%
  summarise(n = sum(!is.na(log_po_corrected))) %>%
  pull(n)

m_n_po <- male_po %>%
  group_by(os_temp) %>%
  summarise(n = sum(!is.na(log_po_corrected))) %>%
  pull(n)

# Assign group sizes
f_n1_po <- f_n_po[1]
f_n2_po <- f_n_po[2]

m_n1_po <- m_n_po[1]
m_n2_po <- m_n_po[2]

# Standard error of Cohen's d
SE_f_po <- sqrt((f_n1_po + f_n2_po) / (f_n1_po * f_n2_po) + (d_f_po^2 / (2 * (f_n1_po + f_n2_po - 2))))
SE_m_po <- sqrt((m_n1_po + m_n2_po) / (m_n1_po * m_n2_po) + (d_m_po^2 / (2 * (m_n1_po + m_n2_po - 2))))

# Contrast between effect sizes
contrast_po <- d_f_po - d_m_po

# SE of contrast
SE_contrast_po <- sqrt(SE_f_po^2 + SE_m_po^2)

# t statistic
t_value_po <- contrast_po / SE_contrast_po

# Welch-style df
df_f_po <- f_n1_po + f_n2_po - 2
df_m_po <- m_n1_po + m_n2_po - 2

df_welch_po <- (SE_f_po^2 + SE_m_po^2)^2 /
  ((SE_f_po^4 / df_f_po) + (SE_m_po^4 / df_m_po))

# p-value
p_value_po <- 2 * pt(-abs(t_value_po), df_welch_po)

# output
c(
  female_d = d_f_po,
  male_d = d_m_po,
  contrast = contrast_po,
  SE_contrast = SE_contrast_po,
  t_value = t_value_po,
  df = df_welch_po,
  p_value = p_value_po
)

#######################################
### offspring temp _ lytic activity ###
#######################################

# Cohen's d
f_eff_ly <- cohens_d(lytic_corrected ~ os_temp, data = female_ly)
m_eff_ly <- cohens_d(lytic_corrected ~ os_temp, data = male_ly)

f_eff_ly
m_eff_ly
# Extract d values
d_f_ly <- f_eff_ly$Cohens_d[1]
d_m_ly <- m_eff_ly$Cohens_d[1]

# Sample sizes per os_temp group
f_n_ly <- female_ly %>%
  group_by(os_temp) %>%
  summarise(n = sum(!is.na(lytic_corrected))) %>%
  pull(n)

m_n_ly <- male_ly %>%
  group_by(os_temp) %>%
  summarise(n = sum(!is.na(lytic_corrected))) %>%
  pull(n)

# Assign group sizes
f_n1_ly <- f_n_ly[1]
f_n2_ly <- f_n_ly[2]

m_n1_ly <- m_n_ly[1]
m_n2_ly <- m_n_ly[2]

# Standard error of Cohen's d
SE_f_ly <- sqrt((f_n1_ly + f_n2_ly) / (f_n1_ly * f_n2_ly) + (d_f_ly^2 / (2 * (f_n1_ly + f_n2_ly - 2))))
SE_m_ly <- sqrt((m_n1_ly + m_n2_ly) / (m_n1_ly * m_n2_ly) + (d_m_ly^2 / (2 * (m_n1_ly + m_n2_ly - 2))))

# Contrast between effect sizes
contrast_ly <- d_f_ly - d_m_ly

# SE of contrast
SE_contrast_ly <- sqrt(SE_f_ly^2 + SE_m_ly^2)

# t statistic
t_value_ly <- contrast_ly / SE_contrast_ly

# Welch-style df
df_f_ly <- f_n1_ly + f_n2_ly - 2
df_m_ly <- m_n1_ly + m_n2_ly - 2

df_welch_ly <- (SE_f_ly^2 + SE_m_ly^2)^2 /
  ((SE_f_ly^4 / df_f_ly) + (SE_m_ly^4 / df_m_ly))

# p-value
p_value_ly <- 2 * pt(-abs(t_value_ly), df_welch_ly)

# output
c(
  female_d = d_f_ly,
  male_d = d_m_ly,
  contrast = contrast_ly,
  SE_contrast = SE_contrast_ly,
  t_value = t_value_ly,
  df = df_welch_ly,
  p_value = p_value_ly
)

```
## Figure - effect size
```{r}
EFF=read.table(file="effect_size.csv",header = TRUE,sep=",")
EFF$sex<-factor(EFF$sex, levels=c("female","male"))

########################
## offspring temp -PO ## Figure 2A
########################
off_temp_PO <- ggplot(EFF, aes(x = sex, y = PO_off, ymin = PO_off_low, ymax = PO_off_high,fill = sex, shape=sex))+ geom_pointrange(linewidth = 1 ,size=1,stroke=1,color="black")+scale_fill_manual(values = alpha(c("black", "white")))+scale_shape_manual(values = c(21,21))
off_temp_PO

off_temp_PO +scale_y_continuous(position = "right",breaks=seq(-0.6, 0.6, 0.3),limits=c(-0.6,0.6))+scale_x_discrete(labels = NULL)+labs(x="", y="")+theme_test()+theme(text = element_text(size=),axis.text.y = element_text(size = 0),legend.position="none",axis.ticks.x = element_blank(),panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1.5))

###########################
## offspring temp -lytic ## Figure 2B
###########################
off_temp_ly <- ggplot(EFF, aes(x = sex, y = ly_off, ymin = ly_off_low, ymax = ly_off_high,fill = sex, shape=sex))+ geom_pointrange(linewidth = 1 ,size=1,stroke=1,color="black")+scale_fill_manual(values = alpha(c("black", "white")))+scale_shape_manual(values = c(21,21))
off_temp_ly

off_temp_ly  +scale_y_continuous(position = "right",breaks=seq(-0.6, 0.6, 0.3),limits=c(-0.6,0.6))+scale_x_discrete(labels = NULL)+labs(x="", y="")+theme_test()+theme(text = element_text(size=),axis.text.y = element_text(size = 0),legend.position="none",axis.ticks.x = element_blank(),panel.border = element_rect(colour = "black",
                                fill = NA,
                                linewidth = 1.5))

```

